Towards Verifying the Bitcoin-S Library

### 2019-06-21 paper/paper.tex
more stainless error outputs

Stainless output:
\begin{lstlisting}[style=stainless]
  [Warning ] Code.scala:9:3: Could not extract tree in class: type A =
             BigInt (class scala.reflect.internal.Trees$TypeDef)
             type A = BigInt
             ^^^^^^^^^^^^^^^
\end{lstlisting}

@@

Stainless output:
\begin{lstlisting}[style=stainless]
  [ Error  ] Code.scala:22:14: Unknown call to & on result (BigInt) with arguments
             List(Number.this.andMask) of type List(BigInt)
            require((result & andMask) == result,
                    ^^^^^^^^^^^^^^^^
\end{lstlisting}

@@

Stainless output:
\begin{lstlisting}[style=stainless]
  [Warning ] Code.scala:90:3: Could not extract tree in class: case private
             class SatoshisImpl extends Satoshis with Product with Serializable {
\end{lstlisting}

>>>>

Stainless output:
\begin{lstlisting}[style=stainless]
  [Warning ] number/NumberType.scala:9:3: Could not extract tree in class: type A = BigInt (class scala.reflect.internal.Trees$TypeDef)
               type A = BigInt
               ^^^^^^^^^^^^^^^

@@

Stainless output:
\begin{lstlisting}[style=stainless]
  [ Error  ] number/NumberType.scala:33:14: Unknown call to & on result (BigInt) with arguments List(Number.this.andMask) of type List(BigInt)
               require((result & andMask) == result,
                       ^^^^^^^^^^^^^^^^

@@

Stainless output:
\begin{lstlisting}[style=stainless]
  [Warning ] currency/CurrencyUnits.scala:36:3: Could not extract tree in class: case private class SatoshisImpl extends Satoshis with Product with Serializable {
  [Warning ]   <caseaccessor> <paramaccessor> private[this] val underlying: addition.modified.number.Int64 = _;
  [Warning ]   <stable> <caseaccessor> <accessor> <paramaccessor> def underlying: addition.modified.number.Int64 = SatoshisImpl.this.underlying;
  [Warning ]   def <init>(underlying: addition.modified.number.Int64): addition.modified.currency.Satoshis.SatoshisImpl = {
  [Warning ]     SatoshisImpl.super.<init>();
  [Warning ]     ()
  [Warning ]   };
  [Warning ]   <synthetic> def copy(underlying: addition.modified.number.Int64 = underlying): addition.modified.currency.Satoshis.SatoshisImpl = new SatoshisImpl(underlying);
  [Warning ]   <synthetic> def copy$default$1: addition.modified.number.Int64 = SatoshisImpl.this.underlying;
  [Warning ]   override <synthetic> def productPrefix: String = "SatoshisImpl";
  [Warning ]   <synthetic> def productArity: Int = 1;
  [Warning ]   <synthetic> def productElement(x$1: Int): Any = x$1 match {
  [Warning ]     case 0 => SatoshisImpl.this.underlying
  [Warning ]     case _ => throw new IndexOutOfBoundsException(x$1.toString())
  [Warning ]   };
  [Warning ]   override <synthetic> def productIterator: Iterator[Any] = runtime.this.ScalaRunTime.typedProductIterator[Any](SatoshisImpl.this);
  [Warning ]   <synthetic> def canEqual(x$1: Any): Boolean = x$1.$isInstanceOf[addition.modified.currency.Satoshis.SatoshisImpl]();
  [Warning ]   override <synthetic> def hashCode(): Int = ScalaRunTime.this._hashCode(SatoshisImpl.this);
  [Warning ]   override <synthetic> def toString(): String = ScalaRunTime.this._toString(SatoshisImpl.this);
  [Warning ]   override <synthetic> def equals(x$1: Any): Boolean = SatoshisImpl.this.eq(x$1.asInstanceOf[Object]).||(x$1 match {
  [Warning ]   case (_: addition.modified.currency.Satoshis.SatoshisImpl) => true
  [Warning ]   case _ => false
  [Warning ] }.&&({
  [Warning ]     <synthetic> val SatoshisImpl$1: addition.modified.currency.Satoshis.SatoshisImpl = x$1.asInstanceOf[addition.modified.currency.Satoshis.SatoshisImpl];
  [Warning ]     SatoshisImpl.this.underlying.==(SatoshisImpl$1.underlying).&&(SatoshisImpl$1.canEqual(SatoshisImpl.this))
  [Warning ]   }))
  [Warning ] } (class scala.reflect.internal.Trees$ClassDef)
                private case class SatoshisImpl(underlying: Int64) extends Satoshis
                ^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^
\end{lstlisting}
